#Introduction 
 
 Article: https://projects.fivethirtyeight.com/redlining/
 
The data presented derives from a study conducted on the continuation of redlining 
where the historical use of the HOLC grading system based on race population that determined
what areas were best (graded A) or desirable (graded B) to invest in (mostly white areas), 
and those that were declining (graded C) or hazardous (graded D) (mostly black areas) still are
prevalent in the segregation of many cities.

This data analysis looks into the segregation of the cities of upstate New York
relative to their HOLC graded living areas 



#Loading Packages & Reading data
```{r}
library(tidyverse)
library(RCurl)
 x <- getURL("https://raw.githubusercontent.com/fivethirtyeight/data/master/redlining/metro-grades.csv")
 redlining_data <- read.csv(text = x)

```

#Creating NY Subset
```{r}
ny_redlining <- redlining_data %>%
  select("metro_area", "holc_grade", "pct_white", "pct_black", "pct_hisp", 
         "pct_asian", "pct_other") %>%
  filter(grepl("NY", metro_area)) %>%
  mutate(pct_nonwhite_sum = rowSums(across(c(pct_black, pct_hisp, pct_asian, pct_other))))

```

#Checking for Missing Variables
```{r}
sum(is.na(redlining_data))

```

#Comparing HOLC Grade between White and Non White population percentages
```{r}
df <- ny_redlining %>%
  select("metro_area", "holc_grade", "pct_white", "pct_nonwhite_sum")

unique(df$metro_area)
```

#Regions designated as grade A by HOLC
```{r}
a_b <- df %>%
  filter(grepl("A|B", holc_grade)) 


print("Average Percentage of White People living in greenlined areas (A or B HOLC graded areas)")
mean(a_b$pct_white)

print("average Percentage of Non-White People living in greenlined areas (A or B HOLC graded areas)")
mean(a_b$pct_nonwhite_sum)
```


#Regions designated as grade C and D  by HOLC
```{r}
c_d <- df %>%
  filter(grepl("C|D", holc_grade)) 

print("Average Percentage of White People living in redlined areas (C or D HOLC graded areas)")
mean(c_d$pct_white)

print("Average of Percentage of Non-White People living in redlined (C or D HOLC graded areas)")
mean(c_d$pct_nonwhite_sum)
```


#Conclusion

In the 6 upstate NY cities used to investigate the continue segregation between 
white and non-white people into greenlined and redlined areas, it was found that
the greenlined areas contained 66.68% of white people vs the 33.32% of non-white people.
For the redlined areas in the investigated cities, it ws found that 44.99% of white 
people lived in these areas white 55.01% lived in the areas. White people
are more likely to reside in areas deemed as investable while racial minorities
are more likely to reside in neglected areas.
To further this study, I recommend gathering average demographic information such 
as average income. By doing so, the segregated areas can be compared to elucidate 
if income differences is a clear distinction between populations.
