
## Intro
The data analyzed in this assignment was movie reviews critiques and their critiques, 
pulled from the New York Times API. The task included accessing the chosen information 
contained in the API for it to then bwe read in the JSON data, and transformed into an 
R DataFrame.

## Importing libraries and retrieving the Data
```{r}
library(tidyverse)
library(httr)
library(rvest)
library(jsonlite)
library(knitr)


response <- GET("https://api.nytimes.com/svc/movies/v2/reviews/search.json?api-key=yNHI7wXwGGegzABJslljTcIvEZuAHVqp")
content <- content(response, "text")
data <- fromJSON(content)
```

## Creating the Dataframe
```{r}
movie_rev <- data.frame(data$results)
movie_rev$link <- movie_rev$link$url
movie_rev <- subset(movie_rev, select = c(-multimedia, -opening_date, -date_updated))

movie_rev$critics_pick <- ifelse(movie_rev$critics_pick == 1, "yes", "no")
knitr::kable(movie_rev, col.names = c("Movie Titles", "MPAA Ratign", "Critics Pick", "Critics", "Review Headline", "Review Summary (Short)", "Publication Date", "Link"))
```

## Analysis
This analysis dives into how each critic critics their reviewed movies. The dataset
was filtered to only analyze those who critiqued more than 1 movie to recognize any
pattern that may arise.
```{r}
 repetitive_critcs <- movie_rev %>%
     arrange(byline) %>%
     filter(duplicated(byline) | duplicated(byline, fromLast = TRUE))
```


```{r}
critiques_count <- repetitive_critcs %>%
  group_by(byline, critics_pick) %>%
  summarize(count = n())
```

##Visualization
```{r}
ggplot(critiques_count, aes(byline, count, fill = critics_pick)) +
  geom_col() +
  scale_fill_manual(values = c("#C80404", "#C804B2")) +
  labs(x = "Critics", y = "Count", fill = "Critic Pick", title ="Diversity in Critics Recommendations") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        plot.title = element_text(hjust = 0.5))
```
```{r}
repetitive_critcs %>%
  filter(byline == "Manohla Dargis")
```

##Conclusion
As shown in the visualization, we see that most critics who analyze movies are 
unannimous in their decision as to whether they would recommenend said movie. The only critic to 
have some diversity within their answers is Manohla Dargis where from the 2 movies 
she reviewed, she recommended 1 (Tori and Lokita) and not the other (John Wick: Chapter 4.

