##Understnding the Market Research job market in NY


```{r}
library(tidyverse)
library(rvest)
library(httr)

```

```{r}
glassdoor_data <- read_html("https://www.glassdoor.com/Job/new-york-ny-us-market-researcher-jobs-SRCH_IL.0,14_IC1132348_KO15,32.htm")

glassdoor_data2 <- read_html("https://www.glassdoor.com/Job/new-york-market-researcher-jobs-SRCH_IL.0,8_IC1132348_KO9,26_IP2.htm?includeNoSalaryJobs=true&pgc=AB4AAYEAHgAAAAAAAAAAAAAAAg5qcyEAKgEBIwYEe7KeHGMytiHAxYlwsaJLw%2FDa9jupwF4%2BbxDi%2Fi6VPifrMWbQEAAA")

glassdoor_data3 <- read_html("https://www.glassdoor.com/Job/new-york-market-researcher-jobs-SRCH_IL.0,8_IC1132348_KO9,26_IP3.htm?includeNoSalaryJobs=true&pgc=AB4AAoEAPAAAAAAAAAAAAAAAAg5qcyEANwECARFgBgttCgQKwJeUTRyooNc2cQFtCqPFMiZMTzWOoIBrxY2NGlz6%2BTeyMGuGZ9HpSsP9vJEAAA%3D%3D")

glassdoor_data4 <- read_html("https://www.glassdoor.com/Job/new-york-market-researcher-jobs-SRCH_IL.0,8_IC1132348_KO9,26_IP4.htm?includeNoSalaryJobs=true&pgc=AB4AA4EAWgAAAAAAAAAAAAAAAg5qcyEAPQECAREuBglx2bsslBRjcmiak3hKtIi5S80ZmFuMh14JzbrbWJ1hmyVdRstgsb5qBvFgP2bolCXAjHVBkEEAAA%3D%3D")
```




## Extracted: Position, Company, Location, Job Posting URL, 
```{r}
job_board <- rep("Glassdoor", 30)

positions1 <- html_nodes(glassdoor_data, ".mt-xsm") %>% html_text()
positions2<- html_nodes(glassdoor_data2, ".mt-xsm") %>% html_text()
positions3<- html_nodes(glassdoor_data3, ".mt-xsm") %>% html_text()
positions4<- html_nodes(glassdoor_data4, ".mt-xsm") %>% html_text()
positions <- c(positions1, positions2, positions3, positions4)

company_name1 <- html_nodes(glassdoor_data, ".job-search-8wag7x") %>% html_text()
company_name2<- html_nodes(glassdoor_data2, ".job-search-8wag7x") %>% html_text()
company_name3<- html_nodes(glassdoor_data3, ".job-search-8wag7x") %>% html_text()
company_name4<- html_nodes(glassdoor_data4, ".job-search-8wag7x") %>% html_text()
company_name <- c(company_name1, company_name2, company_name3, company_name4)
company_name <- str_remove(company_name, "\\d.*")
company_name <- str_remove(company_name, ".job-search-rnnx")

location1 <-html_nodes(glassdoor_data, ".location.mt-xxsm") %>% html_text()
location2<- html_nodes(glassdoor_data2, ".location.mt-xxsm") %>% html_text()
location3<- html_nodes(glassdoor_data3, ".location.mt-xxsm") %>% html_text()
location4<- html_nodes(glassdoor_data4, ".location.mt-xxsm") %>% html_text()
location <- c(location1, location2, location3, location4)
```

```{r}
# Define a function to get pay data that handles missing values
get_pay_data <- function(data) {
  pay_data <- html_nodes(data, ".salary-estimate") %>% html_text()
  
  # Extract the number of job listings on the page
  num_jobs <- length(html_nodes(data, ".jobLink"))
  
  # If the length of pay data is less than the number of jobs, fill with NA
  if (length(pay_data) < num_jobs) {
    missing_pay <- rep(NA, num_jobs - length(pay_data))
    pay_data <- c(pay_data, missing_pay)
  }
  
  return(pay_data)
}

# Extract pay data using the function
pay1 <- get_pay_data(glassdoor_data)
pay2 <- get_pay_data(glassdoor_data2)
pay3 <- get_pay_data(glassdoor_data3)
pay4 <- get_pay_data(glassdoor_data4)
pay <- c(pay1, pay2, pay3, pay4)

pay <- str_remove_all(pay, "\\s\\((Employer est.)\\)|\\s\\((Glassdoor est.)\\)")

pay
```


```{r}
job_urls1 <- glassdoor_data %>%
  html_nodes("a.jobLink") %>%
  html_attr("href") 

job_urls2 <- glassdoor_data2 %>%
  html_nodes("a.jobLink") %>%
  html_attr("href") 

job_urls3 <- glassdoor_data3 %>%
  html_nodes("a.jobLink") %>%
  html_attr("href") 

job_urls4 <- glassdoor_data4 %>%
  html_nodes("a.jobLink") %>%
  html_attr("href") 

job_urls <- c(job_urls1, job_urls2, job_urls3, job_urls4)


job_urls <- unique(job_urls)
job_urls <- str_c("https://www.glassdoor.com", job_urls)
```

```{r}
#Create a list to store the vectors for each URL
job_urlinfo <- list()

# Loop through the URLs and read each page using read_html()
for (i in seq_along(job_urls)) {
  job_urlinfo[[i]] <- read_html(job_urls[i])
}
```

This vector is created to retrieve the conent of the job postings that
will prove essential for the rest of the data scraping.
```{r}
job_req <- list()
for (i in 1:120) {
  job_req[[i]] <- job_urlinfo[[i]] %>% html_elements("#JobDescriptionContainer") %>% html_text()
}
job_req <- unlist(job_req)
```



```{r}
#this extract pay in a different way than before so any missing wages in the first method can then be imported through this method

payx <- list()
for (i in seq_along(job_req)) {
  job_req[[i]] <- str_remove_all(job_req[[i]], "\\b\\d{4}")
  matches <- str_extract_all(job_req[[i]], "\\$?\\d{2,3}(?:[.,]\\d{1,3})?([.]\\d{2})?(?:\\s?-\\s?|\\sto\\s?)?\\$?\\d{2,3}(?:[.,]\\d{1,3})?")
  payx[[i]] <- paste(unlist(matches), collapse = ", ")
}
pay[is.na(pay)] <- payx[is.na(pay)]
```

```{r}
pay <- str_replace_all(pay, "(?i)k", ",000")
pay <- str_remove_all(pay, "(Per Hour)?")
pay <- str_remove_all(pay, "\\s")
add_dash_duplicate <- function(x) {
  if (str_detect(x, "-")) return(x)
    str_replace(x, "(\\$?\\d{2,3}(\\.)?(\\,)?\\d{2,3})", "\\1-\\1")
}
pay <- lapply(pay, add_dash_duplicate)

min_pay <- str_extract_all(pay, "\\$?\\d{2,3}(\\.)?(\\,)?\\d{2,3}(-)")
min_pay <- str_remove_all(min_pay, "-")
max_pay <- str_extract_all(pay, "(-)\\$?\\d{2,3}(\\.)?(\\,)?\\d{2,3}")
max_pay <- str_remove_all(max_pay, "-")


```

```{r}
##converting hourly wages to yearly salary by multiplying hourly wage by 2,080 (full time hours in a year)
min_pay <- str_remove_all(min_pay, "[\\$,]")
matchx <- str_extract_all(min_pay, "(\\d{2})\\.(\\d{2})")
min_pay <- str_remove_all(min_pay, "(\\d{2})\\.(\\d{2})")
matchx <- str_remove_all(matchx, "\\.00")
matchx <- as.numeric(matchx)
matchx <- matchx * 2080
min_pay[min_pay == ""] <- matchx[min_pay == ""]

max_pay <- str_remove_all(max_pay, "[\\$,]")
matchx <- str_extract_all(max_pay, "(\\d{2})\\.(\\d{2})")
max_pay <- str_remove_all(max_pay, "(\\d{2})\\.(\\d{2})")
matchx <- str_remove_all(matchx, "\\.00")
matchx <- as.numeric(matchx)
matchx <- matchx * 2080
max_pay[max_pay == ""] <- matchx[max_pay == ""]
max_pay
```


## Education Requirements
```{r}
educ_req <- list()

for (i in seq_along(job_req)) {
  educ_req[[i]] <- str_extract_all(job_req[[i]], "(?i)(Advanced Degree|Bachelor('s)?|Master('s)?)([(\\s\\w)?(^.(,)?)?\\n]*)?([^.\\n]*)?")
}

```

Degree 
```{r}
degree <- list()

for (i in seq_along(educ_req)) {
  degree[[i]] <- str_extract(educ_req[[i]], "(?i)(Advanced Degree|Degree|Bachelor('s)?|Master('s)?)")
}
```



Major
```{r}
major <- list()

for (i in seq_along(educ_req)) {
  matches <- str_extract_all(educ_req[[i]], "(?i)(Marketing|Advertising|Statistics|Finance|Data Science|Information Science|Information Technology|Operation(s)? Research| Mathematics|Math|ScienceEconomics|Engineering|Business|management information system|human resource|psychology|Supply Chain Management|Health Information Management | Marketing|Advertising|Statistics|Business Administration|Data Science|Economics|Psychology|Sociology|Mathematics|Market Research|Analytics|Information Systems|Communication|Public Relations|Journalism|Finance|Consumer Behavior|Digital Media|Management|Operations Research|Social Sciences|Business Analytics|Behavioral Economics|Anthropology|International Business)")
  major[[i]] <- paste(unlist(matches), collapse = ", ")
}

```


## Skiils
```{r}
skills <- list()

for (i in seq_along(job_req)) {
  skills[[i]] <- str_extract_all(job_req[[i]], "((R\\s)|(?i)(Requirement(s)?|Experience|Qualification(s)?|Python|SoTA|NLP|Natural Language Processing|\\bAI|Artificial Intelligence|\\bML|Machine Learning|PyTorch|Tensorflow|SQL|Power BI|Tableau|Data Visualization|Data Analysis|Statistical|statistic|Google|SAP|Github|Excel)[^.\\n]*)")
}

skills <- str_remove_all(skills, " ")

skills <- sapply(skills, paste, collapse = ", ")
```

extracted skills
```{r}
extracted_skills <- list()

for (i in seq_along(skills)) {
  matches <- str_extract_all(skills[[i]],  "(R\\s)|(?i)(Python|SoTA|NLP|Natural Language Processing|\\bAI|Artificial Intelligence|\\bML\\b|Machine Learning|PyTorch|Tensorflow|SQL|Power BI|Tableau|Data Visualization|Data Analysis|Statistical|statistic|Google|SAP|Github|Excel|Data Analysis|Statistical Analysis|Qualitative Research|Quantitative Research|Survey Design|Focus Group Moderation|Data Visualization|Report Writing|SPSS|Excel|Presentation Skills|SQL|SAS|Data Collection|Market Segmentation|Competitive Analysis|Customer Insight|Predictive Modeling|Tableau|Cross-tabulation|Ethnographic Research|Multivariate Analysis|Data Interpretation|Questionnaire Design|Python|A/B Testing|Project Management|Communication Skills|Consumer Behavior Analysis)")
  extracted_skills[[i]] <- paste(unlist(matches), collapse = ", ")
}
library(stringr)

extracted_skills <- list()

for (i in seq_along(skills)) {
  matches <- str_extract_all(skills[[i]], "(R\\s)|(?i)(Python|SoTA|NLP|Natural Language Processing|\\bAI\\b|Artificial Intelligence|\\bML\\b|Machine Learning|PyTorch|Tensorflow|SQL|Power BI|Tableau|Data Visualization|Data Analysis|Statistical|statistic|Google|SAP|Github|Excel|Statistical Analysis|Qualitative Research|Quantitative Research|Survey Design|Focus Group Moderation|Report Writing|SPSS|Presentation Skills|SAS|Data Collection|Market Segmentation|Competitive Analysis|Customer Insight|Predictive Modeling|Cross-tabulation|Ethnographic Research|Multivariate Analysis|Data Interpretation|Questionnaire Design|A/B Testing|Project Management|Communication Skills|Consumer Behavior Analysis)")
  extracted_skills[[i]] <- paste(unlist(matches), collapse = ", ")
}

relabelled_skills <- lapply(extracted_skills, function(skill) {
  skill <- str_replace_all(skill, "(?i)(Python|PyTorch|Tensorflow)", "Python")
  skill <- str_replace_all(skill, "(?i)(\\bAI\\b|Artificial Intelligence)", "AI")
  skill <- str_replace_all(skill, "(?i)(\\bML\\b|ML\\s|Machine Learning|Predictive Modeling)", "ML")
  skill <- str_replace_all(skill, "(?i)(Natural Language Processing|\\bNLP\\b)", "NLP")
  skill <- str_replace_all(skill, "(?i)Data Visualization", "Data Viz")
  skill <- str_replace_all(skill, "(?i)(Data Analysis|Data Interpretation)", "Data Analysis")
  skill <- str_replace_all(skill, "(?i)(Statistical|statistic|Cross-tabulation|Multivariate Analysis)", "Stat Analysis")
  skill <- str_replace_all(skill, "(?i)(Qualitative Research|Ethnographic Research|Focus Group Moderation)", "Qual Research")
  skill <- str_replace_all(skill, "(?i)(Quantitative Research|Survey Design)", "Quant Research")
  skill <- str_replace_all(skill, "(?i)(Excel)", "Excel")
  skill <- str_replace_all(skill, "(?i)Presentation Skills", "Presentation")
  skill <- str_replace_all(skill, "(?i)(Data Collection|Data Entry)", "Data Collection")
  skill <- str_replace_all(skill, "(?i)Questionnaire Design", "Questionnaire")
  skill <- str_replace_all(skill, "(?i)A/B Testing", "A/B Testing")
  skill <- str_replace_all(skill, "(?i)Project Management", "Proj Management")
  skill <- str_replace_all(skill, "(?i)Communication Skills", "Communication")
    skill <- str_replace_all(skill, "R|R\\s", "Communication")
  return(skill)
})
```


##Years of Experience
```{r}
library(stringr)
# 1. Extract years of experience details
years_experience <- list()

for (i in seq_along(job_req)) {
  matches <- str_extract_all(job_req[[i]], "(?i)\\d+-?\\d*\\+?\\s*year((')?s)?")
  years_experience[[i]] <- paste(unlist(matches), collapse = ", ")
}

# 2. Cleaning up years_experience
years_experience <- lapply(years_experience, function(x) {
  x <- str_remove_all(x, "(\\d{2}\\+?)|(years|year)")
  x <- str_replace_all(x, "[-+]", "")
  return(x)
})

# 3. Calculate the average of digits in each string
calculate_average <- function(x) {
  digits <- unlist(str_extract_all(x, "\\d")) # Extract individual digits
  if(length(digits) == 0) return(NA) # Handle cases with no digits
  sum(as.numeric(digits)) / length(digits)
}

years_experience <- lapply(years_experience, calculate_average)
years_experience <- as.numeric(years_experience)
```



## Work Enviornment
extract In-person, Remote, or Hybrid strings 
```{r}
work_environment <- list()

# First loop to find matches
for (i in seq_along(job_req)) {
  matches <- str_extract_all(job_req[[i]], "(?i)(Remote|In-Person|In Person|On-Location|On location|Hybrid)")
  
  if(length(unlist(matches)) == 0) {
    work_environment[[i]] <- "In-Person"
  } else {
    work_environment[[i]] <- paste(unlist(matches), collapse = ", ")
  }
}

# String replacements
work_environment <- lapply(work_environment, function(location) {
  location <- str_replace_all(location, "(?i)(In-Person|In Person|On-Location|On location)", "In Person")
  location <- str_replace_all(location, "(?i)(Remote|remote)", "Remote")
  location <- str_replace_all(location, "(?i)(Hybrid|hybrid)", "Hybrid")
  return(location)
})
work_environment
```

## Seniority
extract Entry-level, Associate, Junior, or Senior strings.
the identification of what positions are under what seniority level was
determined by referencing the Indeed article:
https://www.indeed.com/career-advice/career-development/seniority-level

```{r}
# Define a function to get pay data that handles missing values


seniority_lvl <- list()

for (i in seq_along(job_req)) {
  matches <- str_extract_all(job_req[[i]], "(?i)(Entry|Assistant|Intern|Trainee|Associate|Manager|Lead |Officer|Supervisor|Junior|Senior|Executive|\\bVP|Vice President|Architect)")
  capitalized_matches <- unlist(str_extract_all(unlist(matches), "\\b[A-Z][a-z]*\\b"))
  seniority_lvl <- str_remove_all(seniority_lvl, ",.*")
  seniority_lvl[[i]] <- paste(capitalized_matches, collapse = ", ")
}
head(seniority_lvl)


#back up seniority data from alternative method
seniority_lvlX <- list()
for (i in seq_along(positions)) {
  matches <- str_extract_all(positions[[i]], "(?i)(Entry|Assistant|Intern |Trainee|Associate|Manager|Lead |Officer|Supervisor|Junior|Senior|Executive|\\bVP|Vice President|Architect)")
  capitalized_matches <- unlist(str_extract_all(unlist(matches), "\\b[A-Z][a-z]*\\b"))
  seniority_lvlX <- str_remove_all(seniority_lvlX, ",.*")
  seniority_lvlX[[i]] <- paste(capitalized_matches, collapse = ", ")
}
head(seniority_lvlX)

#filling in some missing data
for (i in seq_along(seniority_lvl)) {
  if (trimws(seniority_lvl[[i]]) == "") {
    seniority_lvl[[i]] <- seniority_lvlX[[i]]
  }
}
```

```{r}

#relabeling seniority data
relabelled_seniority_lvl <- lapply(seniority_lvl, function(role) {
  ifelse(role %in% c("Entry", "Intern", "Trainee", "Assistant", "Junior"), "Entry-Level",
    ifelse(role %in% c("Associate", "Lead", "Supervisor", "Architect"), "Mid-Level",
      ifelse(role %in% c("Senior", "Manager"), "Senior-Level", "Undefined")))
})

# Convert list to a character vector if necessary
relabelled_seniority_lvl <- unlist(relabelled_seniority_lvl)

relabelled_seniority_lvl


```

```{r}
positions <- str_remove_all(positions, "\\|.*")
```

##Unlisting to create a dataframe
```{r}
work_environment <- unlist(work_environment)
relabelled_skills <- unlist(relabelled_skills)
years_experience <- unlist(years_experience)
pay <- unlist(pay)
min_pay <- unlist(min_pay)
max_pay <- unlist(max_pay)
degree <- unlist(degree)
major <- unlist(major)
```

##Creating a dataframe 
```{r}
data <- data.frame(positions, relabelled_seniority_lvl, company_name, location, work_environment, pay, min_pay, max_pay, degree, major, relabelled_skills, years_experience,  job_urls)
data
```


```{r}
data <- data %>%
  mutate(major = gsub("\\.", ",", major)) %>%
  separate_rows(major, sep = ",") %>%
  mutate(relabelled_skills = gsub("\\.", ",", relabelled_skills)) %>%
  separate_rows(relabelled_skills, sep = ",") %>%
   mutate(work_environment = gsub("\\.", ",", work_environment)) %>%
  separate_rows(work_environment, sep = ",") %>%
  mutate(years_experience = gsub("\\.", ",", years_experience)) %>%
  separate_rows(years_experience, sep = ",")

data <- distinct(data) 
data <- data %>% drop_na()
data
```
##Wordcloud
```{r}
library(wordcloud)

wordcloud(data$relabelled_skills, min.freq = 1, max.words=200, random.order=FALSE, rot.per=0.35, colors=brewer.pal(8, "Dark2"))

wordcloud(data$major, min.freq = 1, max.words=200, random.order=FALSE, rot.per=0.35, colors=brewer.pal(8, "Dark2"))
```
```{r}
data$relabelled_skills <- trimws(data$relabelled_skills)
data$relabelled_skills <- tolower(data$relabelled_skills)
data$relabelled_skills <- gsub("[^[:print:]]", "", data$relabelled_skills)

# Remove rows where relabelled_skills is an empty string
data <- data %>%
  filter(relabelled_skills != "")

# Get distinct skills
distinct_skills <- data %>%
  distinct(relabelled_skills) %>%
  pull(relabelled_skills)

data$work_environment <- trimws(data$work_environment)
data$work_environment <- tolower(data$work_environment)
data$work_environment <- gsub("[^[:print:]]", "", data$work_environment)

distinct_skills <- data %>%
  distinct(work_environment) %>%
  pull(work_environment)

data <- data %>% drop_na()

data %>%
  distinct(positions, company_name)
```

##Cleaned dataset (N=45)
```{r}
data
```


```{r}

library(forcats)

df_plot <- data %>%
  select(positions, company_name, relabelled_seniority_lvl, relabelled_skills) %>%
  distinct(positions, company_name, relabelled_seniority_lvl, relabelled_skills) %>%
  add_count(relabelled_skills) %>%
  top_n(200, n) 

df_plot$relabelled_skills <- fct_reorder(df_plot$relabelled_skills, df_plot$n)

ggplot(df_plot, aes(relabelled_skills)) +
  geom_bar() +
  coord_flip()
```

```{r}
data %>%
  select(positions, company_name, relabelled_seniority_lvl) %>%
  distinct(positions, company_name, relabelled_seniority_lvl) %>%
  ggplot(aes(relabelled_seniority_lvl)) +
  geom_bar()
         
data %>%
  select(positions, company_name, relabelled_seniority_lvl) %>%
  distinct(positions, company_name, relabelled_seniority_lvl) %>%
  filter(relabelled_seniority_lvl != "Undefined") %>%
  ggplot(aes(relabelled_seniority_lvl)) +
  geom_bar()
```

```{r}
data %>%
  select(positions, company_name, work_environment) %>%
  distinct(positions, company_name, work_environment) %>%
  ggplot(aes(work_environment)) +
  geom_bar()
```

## Questions to answer
What's the relationship between...
- Seniority level and minimum pay
- Years of experience and minimum pay
- Work Location and minimum pay
- Degree + Years of experience and minimum pay
- Skill demand and Seniority

```{r}
library(knitr)
relabelled_skills <- str_remove_all(relabelled_skills, "\\s")

data %>%
  filter(relabelled_seniority_lvl == "Mid-Level") %>%
  distinct(positions, company_name, relabelled_skills) %>%
  count(relabelled_skills, name = "skill_count") %>%
  arrange(desc(skill_count)) %>%
  mutate("Percentage of Postings" = paste0(round((skill_count / sum(skill_count)) * 100, 2), "%")) %>%
  select(-skill_count) %>%
  kable( caption = "Top Skills for Mid-Level Market Researchers (N = 8)", align=c('l', 'r'), col.names = c("Skills", "Percentage of Postings"))
```

```{r}
data %>%
  filter(relabelled_seniority_lvl == "Senior-Level") %>%
  distinct(positions, company_name, relabelled_skills) %>%
  count(relabelled_skills, name = "skill_count") %>%
  arrange(desc(skill_count)) %>%
  mutate("Percentage of Postings" = paste0(round((skill_count / sum(skill_count)) * 100, 2), "%")) %>%
  select(-skill_count) %>%
  kable( caption = "Top Skills for Mid-Level Market Researchers (N = 20)", align=c('l', 'r'), col.names = c("Skills", "Percentage of Postings"))
```

```{r}
data %>%
  filter(relabelled_seniority_lvl == "Undefined") %>%
  distinct(positions, company_name, relabelled_skills) %>%
  count(relabelled_skills, name = "skill_count") %>%
  arrange(desc(skill_count)) %>%
  mutate("Percentage of Postings" = paste0(round((skill_count / sum(skill_count)) * 100, 2), "%")) %>%
  select(-skill_count) %>%
  kable( caption = "Top Skills for Market Researchers' Undefined (N = 20)", align=c('l', 'r'), col.names = c("Skills", "Percentage of Postings"))
```
##coorelation between years of experience and pay
```{r}
data$min_pay <- as.numeric(data$min_pay)
data$years_experience <- as.numeric(data$years_experience)

cor_test <- cor.test(data$years_experience, data$min_pay)

print(cor_test)

```


